Verifying Demonstrations

### 2018-02-25 paper/analysis.tex
Adds AnonPass, thus we can use their performance evals

\mode<presentation>{%
\begin{frame}
  \begin{center}
    Alice $:=$ Alice's cryptographic device
  \end{center}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{assumption}[During protest]
    \begin{itemize}
      \item Everyone has a smartphone.
      \item Can use ad-hoc networks during the event.
      \item Computations bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause{}

  \begin{assumption}[Before and after protest]
    \begin{itemize}
      \item Internet connection available.
      \item Computations not bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause{}

  \begin{remark}
    We provide a lower bound, since there might be participants without phones.
  \end{remark}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{itemize}
    \item Eve wants to arrange a counter-protest.
    \item She wants to steal some of Alice's participants' proofs.
    \item To do this she must have an identifier that matches.
    \item I.e.\ she must find a second preimage for the hash function.
  \end{itemize}
\end{frame}
}

@@

>>>>

@@

@@

@@

\subsection{Threshold of witnesses}

Assume that every person has 5000 contacts in their contact 
book~\cite{DifficultyOfPrivateContactDiscovery}.
Then it would be reasonable to set the threshold of at least 6000 witnesses.
According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
\SI{2.66}{\giga\hertz} Core 2 processor.
This yields \(
  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
  \SI{48}{\second}.
\) of processing.
